Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-08-15 chatbot_classification/aaai_2021/paper.tex
modification based on ver_1 and update experimental results
update experimental results

@@

ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.614$} & \multirow{2}*{$0.809$} & \multirow{2}*{$0.853$} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2735$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.6217$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline

@@

2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline

@@

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
\hline
\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & $0.8124$ & 0.05 & 0.05 & 0.05\tabularnewline
\cline{2-7}
\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.8114$ & 0.05 & 0.05 & 0.05\tabularnewline
\hline
\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & $0.7364$ & 0.05 & 0.05 & 0.05\tabularnewline
\cline{2-7}
\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.7445$ & 0.05 & 0.05 & 0.05\tabularnewline
\hline
\end{tabular}
\par\end{centering}
\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}

@@

\textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines. As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by 10 percents, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets. In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying. As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of +7.81 percents on average. Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model. These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.

>>>>

LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline

@@

ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.6345$} & \multirow{2}*{$0.8090$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.3549$} & \multirow{2}*{$0.3876$} & \multirow{2}*{$0.5808$} & \multirow{2}*{$0.6320$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline

@@

2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline

@@

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
\hline
\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & - & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
\cline{2-7}
\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.8114$ & - & - & $0.7826$\tabularnewline
\hline
\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & - & $0.7364$ & - & - & -\tabularnewline
\cline{2-7}
\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.7445$ & - & - & -\tabularnewline
\hline
\end{tabular}
\par\end{centering}
\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}

@@

\textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines. As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by +17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task. Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets. In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying. As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of +7.81 percents on average. Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model. These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.
